\scshape Topics in mechanism design

### 2025-12-07 ch3.tex
Add files via upload

A different way of thinking about limited commitment is that absent commitment, the agent and principal simply play a game: in particular, a repeated game of incomplete information, with the private information on one side only.
Each equilibrium of this game induces some allocation,%
	\footnote{Note that equilibria can differ off the path of play, but still induce the same allocation.}
and optimal incentive-provision from the principal's perspective
amounts to playing a principal-preferred equilibrium.

@@

\paragraph{The literature.} \textcite{LipnowskiRamos2020} characterise principal-optimal equilibria (and more generally, Pareto-optimal equilibria).%
	\footnote{In their model, the agent learns $T_n$ only if and when she is offered the good in period $n$. This does not make a difference, I believe.
	For suppose the principal-preferred equilibrium were to feature the agent conditioning her behaviour in period $n+1$
	on what $T_n$ was if she was not offered the good in period $n$.
	Since $T_n$ has no statistical effect on $T_{n+1}$ (that's our IID assumption),
	this just amounts to the agent randomising in period $n+1$ (when the principal did not offer the good in period $n$);
	so we can replicate this behaviour by having the agent mix (i.e. she can use her own set of dice to randomise, instead of conditioning her behaviour on the `natural dice' $T_n$).}
Their analysis relies on the `APS' technique \parencite{AbreuPearceStacchetti1990}, which provides a recursive formulation of repeated games with imperfect monitoring. This is a standard (indeed, essential!) tool for analysing repeated interactions without commitment.
The original APS paper is rather beautiful,
but you may prefer to learn it from the textbook treatment of \textcite{MailathSamuelson2006}, or from whatever lecture notes you can find around the internet.
Another nice paper on dynamic allocation without commitment is \textcite{DeclippelEliazFershtmanRozen2021}, who study a model with \emph{two} agents.

>>>>

A different way of thinking about limited commitment is that absent commitment, the agent and principal simply play a game: in particular, a repeated game of incomplete information, with the private information on one side only.
Each equilibrium of this game induces some allocation,%
	\footnote{Note that two equilibria which induce the same allocation can still differ off the path of play.}
and optimal incentive-provision from the principal's perspective
amounts to playing a principal-preferred equilibrium.

@@

\paragraph{The literature.} \textcite{LipnowskiRamos2020} characterise principal-optimal equilibria (and more generally, Pareto-optimal equilibria).%
	\footnote{In their model, the agent learns $T_n$ only if and when she is offered the good in period $n$. This does not make a difference, I believe.
	For suppose the principal-preferred equilibrium were to feature the agent conditioning her behaviour in period $n+1$
	on what $T_n$ was if she was not offered the good in period $n$.
	Since $T_n$ has no statistical effect on $T_{n+1}$ (that's our IID assumption),
	this just amounts to the agent randomising in period $n+1$ (when the principal did not offer the good in period $n$);
	so we can replicate this behaviour by having the agent mix (i.e. she can use her own set of dice to randomise, instead of conditioning her behaviour on the `natural dice' $T_n$).}
Their analysis relies on the `APS' technique \parencite{AbreuPearceStacchetti1990}, which provides a recursive formulation of repeated games with imperfect monitoring. This is a standard (indeed, essential!) tool for analysing repeated interactions without commitment. I have lecture notes on APS, as it happens \parencite[chapter~6 in][]{gt}.
Another nice paper on dynamic allocation without commitment is \textcite{DeclippelEliazFershtmanRozen2021}, who study a model with \emph{two} agents.
